---
title: "Integration of R and Python"
author: "Mussa Ngosha: Data Scientist"
date: "3/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Data scientists are highly interested to discover knowledge and extract insights from the data. R and Python are the robust languages that are frequently used when working with data. However, some Data scientists prefer to use only one language. Moreover, there is no a clear reason of why some Data Scientists do prefer only one language instead of the other?, to me I understand that, its an issue of Camps like R camps and Python camps whereby members are only competent in such either language. Furthermore, for those who are interested to use both R and Python, instead of coding in different notebooks, there is R package called 'reticulate': This package provides a significant number of tools that allows scientists to work with data using R and Python on the same environment:
++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

HOW TO SETUP R AND PYTHON ON THE SAME ENVIRONMENT
+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
STEPS:
1. Install Reticulate package

   install.package('reticulate')


2. Load the library

   require(reticulate)
   
3. Connect R and python

   use_python(Indicate the directory where python is installed)
   
   
+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

```{r}
### Example of Setting up R and Python 

### Load reticulate package
require(reticulate)

### Use 'use_python' fuction to specify the python language to be connected
# For Anaconda
use_python("C:/Users/dlab/AppData/Roaming/Microsoft/Windows/Start Menu/Programs/Anaconda3 (64-bit)")
# For python 3.7
use_python("C:/Users/dlab/AppData/Roaming/Microsoft/Windows/Start Menu/Programs/Python 3.7")
```
++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

Note: (i) On the same environment, every language will run on its own chunk like r chunk and python chunk.
      (ii) If you are using Rmarkdown, Ctrl+Alt+I to create a chunk for r, if you want a python chunk, create below            by placing Ctrl+Alt+I, the edit the latter r to python
      
+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

## R chunk
```{r}
### load packages
require(readr)
require(tidyverse)
require(dplyr)
```

### Rython chunk
```{python}
### import packages
import numpy as np
import pandas as pd
import matplotlib.pyplot as plt
```

